---
title: "Visualize Results"
author: "Elise Amblard, Hugo Barbot, Florent Chuffart and Magali Richard"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    self_contained: true
    theme: cayman
    highlight: github
    toc: true
    # toc_float: true
    toc_depth: 3
    number_sections: true
    keep_tex: yes
---


```{r, include=(FALSE)}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
options(knitr.duplicate.label = "allow")

  requiered_packages = c("fmsb")#,"circlize",'knitr') #,"httpuv") #"catools") 

  installed_packages <- installed.packages( )
  for (package in requiered_packages ) {
      if ( !{ package %in% installed_packages } ) {
          print(x = paste("Installation of ", package, sep = "") )
          install.packages(
              pkgs = package
            , repos = "https://cloud.r-project.org"
          )
      } else {
          print(x = paste(package, " is installed.", sep = "") )
      }
      library(package, character.only = TRUE)
  }
  remove(list = c("installed_packages", "package") )
  

knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE)#, results="hide")
options(knitr.duplicate.label = "allow")
```

```{r params}

if (!exists("groundtruth_file"))    {groundtruth_file = "../input/ref/groundtruth_smoothies_fruits.rds"} 
if (!exists("prediction_file"))     {prediction_file =  "../input/res/prediction.rds"       }  
if (!exists("score_file"))          {score_file = "../input/res/scores.rds"       }    

```

```{r read_output}

# prediction = readRDS(  "../input/ref/groundtruth_smoothies_fruits.rds")
# ground_truth = readRDS("../input/res/prediction.rds")


prediction <- readRDS(paste0(input,.Platform$file.sep,"res",.Platform$file.sep,"prediction.rds"))
ground_truth_file = paste0(input, .Platform$file.sep, "ref", .Platform$file.sep, "groundtruth_smoothies_fruits.rds")
ground_truth =  readRDS(file = ground_truth_file )

score_file = paste0(output, .Platform$file.sep, "scores.rds")
score =  readRDS(file = score_file )


# profiling <- readRDS(file = paste0(input, .Platform$file.sep, "res", .Platform$file.sep, "Rprof.rds") )



# prediction = readRDS(prediction_file)
# ground_truth = readRDS(groundtruth_file)
# score = readRDS(score_file)

# greg_tmp = gregexpr("_", prediction_file)
baseline_used = "user baseline"
dataset_used = "smoothie"
```

# Summaries 
## Summary of the prediction

### Heatmap of prediction

```{r Heatmap_pred}
if (is.null(colnames(prediction))) {
  colnames(prediction) = paste0("Sample", format(1:ncol(prediction), digits = ceiling(log10(ncol(prediction)))) )
}

ComplexHeatmap::Heatmap(
  t(prediction),
  col = circlize::colorRamp2(seq(0, 1, length.out = 32), rev(heat.colors(32))),
  column_title = paste("Estimated proportion by", baseline_used, "on dataset", 
                       if (dataset_used == "smoothie") {"smoothies"} else {which(dataset_used == datasets)}),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  heatmap_legend_param = list(title = "Proportion"),
  column_names_rot = 45
)
```


### Boxplot of the absolute bias/error

```{r abs_bias}

abs_bias = abs(prediction - ground_truth)

# colors=viridis::viridis(5)
# 
# ComplexHeatmap::Heatmap(
#   t(abs_bias),
#   col = colorRampPalette(colors)(50),
#   cluster_rows = FALSE,
#   cluster_columns = FALSE,
#   heatmap_legend_param = list(title = "Proportion"),
#   column_names_rot = 45
# )


boxplot(
  t(abs_bias),
  bty = "n",
  col = "tan2",
  xlab = "Cell types",
  ylab = "Absolute bias",
  main = paste("Absolute bias among each cell type by", baseline_used, "on dataset", 
                       if (dataset_used == "smoothie") {"smoothies"} else {which(dataset_used == datasets)})
)



# abs_bias_per_cell_type = rowMeans(abs_bias)
# sd_estim_per_cell_type = apply(proportion, 1, sd)

# Comment FCh: please avoid magrittr, dplyr, tidyr do to a simple boxplot.
# Comment HBa: I personnaly prefer the look of ggplot2

# library(magrittr)
# library(ggplot2)
# abs_bias %>% t() %>% as.data.frame() %>% 
#   tidyr::pivot_longer(
#     everything(),
#     names_to = "Cell_type",
#     values_to = "absolut_bias"
#   ) %>% 
#   dplyr::mutate(
#     Cell_type = factor(Cell_type, levels = rownames(abs_bias))
#   ) %>% 
#   ggplot() +
#   geom_boxplot(aes(x = Cell_type, y = absolut_bias)) +
#   labs(
#     x = "Cell types",
#     y = "Absolut bias",
#     title = "Absolut bias for all bulks per cell types for dataset1"
#   )


```

Boxplot of absolute bias between estimated proportion and ground truth proportion $|\hat{\beta}_{prop} - \beta_{true\_prop}|$ for each cell type. 

## Summary of scores


- Global scores:

```{r scores_global_table,results='asis'}
print(knitr::kable(score$baseline_estimation) )
```


```{r scores_global_radarchart}



# We don't take the global score for the radar chart since it's a proxy of the area
df_radarplot = as.data.frame(rbind(
  c(0,0,1,1,1), # the max value for each var
  c(0.5,0.5,0,0,0), # the min value for each var
  score$baseline_estimation[, -ncol(score$baseline_estimation)]
))
# fmsb::radarchart(df_radarplot)
fmsb::radarchart(df_radarplot, axistype=2 , 
                  # Performance
    title = paste("Score of each metric for", baseline_used, "on dataset", 
                       if (dataset_used == "smoothie") {"smoothies"} else {which(dataset_used == datasets)}),
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9), pfcol=rgb(0.2,0.5,0.5,0.5), plwd=4,
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey50", cglwd=0.8,
 
    #custom labels
    vlcex=0.8
    )

# Comment HB: the visualization by a radar/spider plot is intrinsecly linked to the aggregate score for defining the scope (min and max) for each variable.
```


- Scores per samples:
```{r scores_samples}

df_score_samples = cbind(score$rmse_samples, score$mae_samples, 1-score$pearson_samples)
colnames(df_score_samples) = c("RMSE", "MAE", "1-Pearson")
boxplot(
  df_score_samples,
  bty = "n",
  col = "tan2",
  xlab = "",
  ylab = "",
  main = "Different scoring measures per sample"
)
```

Boxplot of the Root Mean Square Error, the Mean Absolute Error and one minus the pearson's correlation value, calculated for each sample. 



# Session Information

```{r, results="verbatim"}
sessionInfo()
```


